Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation

### 2022-11-10 src/tex/ms.tex
[showyourwork] overleaf sync

% PSFs
The \ac{psf} depends on the successive planes through which light passes from the entrance pupil of the telescope through to the detector. This can be calculated from physical optics: for a simple camera bringing light from the pupil to focus at a detector plane, the \ac{psf} is the Fourier transform of the input wavefront, the regime of Fraunhofer diffraction. In the more general Fresnel regime where the detector is slightly out of focus, there are additional quadratic phase factors before and after this Fourier transform. In more complicated instruments like coronagraphs, the light might pass through multiple re-imaged pupil and focal planes, being operated on in each. In either case, the trouble is that the \ac{psf} is distorted by unknown aberrations - distortions in the wavefront, which can be represented as a spatially-varying phase map across the optical plane.

% Phase Retrieval - G-S, Fienup, review papers, kernel phase

% Pixel Sensitivities - Photometry
% K2
% K2SFF
% K2SC
% EVEREST
% OWL/HALO
% CPM
% LSST
% Pixel Sensitivities - Imaging
% Euclid
% JWST AMI

>>>>

\subsection{Phase Retrieval}
% PSFs
The \ac{psf} depends on the successive planes through which light passes from the entrance pupil of the telescope through to the detector. This can be calculated from physical optics: for a simple camera bringing light from the pupil to focus at a detector plane, the \ac{psf} is the Fourier transform of the input wavefront, the regime of Fraunhofer diffraction. In the more general Fresnel regime where the detector is slightly out of focus, there are additional quadratic phase factors before and after this Fourier transform. In more complicated instruments like coronagraphs, the light might pass through multiple re-imaged pupil and focal planes, being operated on in each. In either case, the trouble is that the \ac{psf} is distorted by unknown aberrations - distortions in the wavefront, which can be represented as a spatially-varying phase map across the optical plane.

% Phase Retrieval - G-S, Fienup, review papers, kernel phase
Phase retrieval is the problem of inferring these aberrations from data, which is in general ill-posed: because of the Hermitian symmetry of the Fourier transform, and because we measure \textit{intensity} and not electric field in optical astronomy, there is a large space of aberrations that would generate the same intensity \ac{psf}. Fortunately, this space can be restricted to physically-realistic solutions and readily solved by algorithms such as the Gerchberg-Saxton algorithm \cite{gerchberg1972}, using ideas from compressed sensing \cite{candes2011}, or by machine learning \cite{metzler2018,isil2019,nishizaki2020}.  Phase retrieval was memorably performed to infer and correct the serious aberration on the \textit{Hubble Space Telescope} mirror at launch \cite{hubble_phase_ret}. 
Earlier work in the vein of this paper has shown that the phase retrieval problem can be efficiently solved by taking a forwards model of physical optics, obtaining partial derivatives with automatic differentiation, and optimizing its parameters by gradient descent \cite{jurling_fienup,phase_ret_and_design}.

\subsection{Detector Calibration}
% Pixel Sensitivities - Photometry
% K2
% K2SFF
% K2SC
% EVEREST
% OWL/HALO
% CPM
% LSST
% Pixel Sensitivities - Imaging
% Euclid
% JWST AMI
